Below is an example of a complete R Markdown (.Rmd) script that incorporates your provided R script. You can save this as, for example, `analysis.Rmd` and then knit it to your desired output format (HTML, PDF, etc.).

```markdown
---
title: "Time Series Forecasting with Holidays and Model Averaging"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

This document demonstrates an end-to-end workflow for time series forecasting by enhancing sales data with holiday events. The process involves:
  
- Loading and merging holiday event data.
- Splitting the time series into training and testing sets.
- Training multiple forecasting models (Prophet, Prophet Boost, and Linear Regression).
- Calibrating and forecasting on the test set.
- Re-fitting models on the full dataset.
- Averaging forecasts from different models for improved performance.

# Setup

Make sure to load the required packages. You may need to install any packages that are not already available in your R environment.

```{r setup, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(lubridate)
library(timetk)
library(modeltime)
library(prophet)
# Other packages (such as xgboost) may be needed depending on your installation

# Set global chunk options
knitr::opts_chunk$set(echo = TRUE)
```

# Data Preparation

First, we load the holiday events data and merge it with the sales data. The `holiday_flag` is created to indicate whether a date corresponds to a holiday event.

```{r load-data}
# Load the holidays events data
holidays_events <- read_csv("Praxis/store-sales-time-series-forecasting/holidays_events.csv")

# Assuming Party_df is pre-loaded with your sales data, merge holiday events
Party_holidays_promo <- Party_df %>% 
  left_join(holidays_events, by = "date") %>% 
  mutate(holiday_flag = ifelse(is.na(type), 0, 1))
```

# Data Splitting

Next, we split the data into training and testing sets using a time series split. The testing set is set to assess one year of data while keeping a cumulative training set.

```{r time-series-split}
splits <- time_series_split(Party_holidays_promo, assess = "1 year", cumulative = TRUE)
```

# Retraining Models

We will train three different models: Prophet, Prophet Boost, and a Linear Regression (LM) model.

## Prophet Model

```{r prophet-model}
Prophet_model <- prophet_reg() %>%
  set_engine("prophet") %>%
  fit(
    sales ~ date + onpromotion + holiday_flag,
    data = training(splits)
  )
```

## Prophet Boost Model

```{r prophet-boost-model}
Prophet_boost_model <- prophet_boost() %>%
  set_engine("prophet_xgboost") %>%
  fit(
    sales ~ date + as.numeric(date) + month(date, label = TRUE) + onpromotion + holiday_flag, 
    data = training(splits)
  )
```

## Linear Regression Model

```{r linear-model}
LM_model <- linear_reg() %>%
  set_engine("lm") %>%
  fit(
    sales ~ as.numeric(date) + month(date, label = TRUE) + onpromotion + holiday_flag,
    data = training(splits)
  )
```

# Modeltime Table and Calibration

The models are then combined into a modeltime table and calibrated on the testing data.

```{r modeltime-table}
model_tbl <- modeltime_table(
  Prophet_model,
  Prophet_boost_model,
  LM_model
)

calibration_tbl <- model_tbl %>%
  modeltime_calibrate(testing(splits))
```

You can review model performance using the accuracy table:

```{r model-accuracy}
calibration_tbl %>%
  modeltime_accuracy() %>%
  table_modeltime_accuracy(resizable = TRUE, bordered = TRUE)
```

# Forecasting

Forecast the future values with the calibrated models and visualize the results.

## Forecast on Testing Data

```{r forecast-testing}
calibration_tbl %>%
  modeltime_forecast(
    new_data = testing(splits),
    actual_data = Party_holidays_promo,
    conf_interval = 0.95
  ) %>%
  plot_modeltime_forecast(.legend_show = TRUE, .legend_max_width = 25)
```

## Refit Models on All Data and Forecast

Refit the calibrated models using the entire dataset and generate forecasts on the testing data.

```{r refit-forecast}
refit_tbl <- calibration_tbl %>%
  modeltime_refit(data = Party_holidays_promo)

forecast_tbl <- refit_tbl %>%
  modeltime_forecast(
    new_data = testing(splits),
    actual_data = Party_holidays_promo,
    conf_interval = 0.95
  )

# Plot interactive forecast if supported by your output device
forecast_tbl %>%
  plot_modeltime_forecast(.interactive = TRUE)
```

# Model Averaging

Here, we perform model averaging by grouping the forecasts (excluding the actual values) and computing the mean prediction along with confidence intervals.

```{r model-averaging}
mean_forcast_tbl <- forecast_tbl %>%
  filter(.key != "actual") %>%
  group_by(.key, .index) %>%  # Group all predictions for one date
  summarise(across(.value:.conf_hi, mean)) %>%  # Compute the mean for each forecast metric
  mutate(
    .model_id = 3,     # Denotes the number of models used
    .model_desc = "Average of Models"
  )

# Combine actual values with the averaged forecasts and plot
forecast_tbl %>%
  filter(.key == "actual") %>%
  bind_rows(mean_forcast_tbl) %>%
  plot_modeltime_forecast()
```

# Accessing the Forecast Values

If you want to inspect the numeric forecast values, you can do so with:

```{r forecast-values}
forecast_tbl$.value
```

# Conclusion

This R Markdown document outlines a complete forecasting workflow that incorporates holiday events into the modeling process. We trained multiple models, calibrated their performance, generated forecasts, and finally applied model averaging to enhance the predictions.

Feel free to adjust the code and add further commentary as needed for your analysis.
```

This script is self-contained and designed to guide you through the steps of data loading, model training, forecasting, and evaluation—all within an R Markdown framework.